quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-15 paper-quollr.Rmd
Added intro image

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

hex_grid_scurve <- ggplotly(hex_grid_scurve, width = "600", 
                     height = "600", tooltip = "none")

df_exe <- comb_data_model(
    highd_data = scurve, 
    model_highd = df_bin_scurve, 
    model_2d = df_bin_centroids_scurve
)

scurve_umap_model_vis <- show_langevitour(
    point_data = df_exe, 
    edge_data = tr_from_to_df_scurve
)
```

@@

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   hex_grid_scurve,
                   scurve_umap_model_vis),
    device = "sm"
  )
```

@@

>>>>

## 2-d vis model
hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#33a02c")

hex_grid_scurve_int <- ggplotly(hex_grid_scurve, 
                                width = "350", 
                                height = "350", 
                                tooltip = "none") |>
  config(
    staticPlot = TRUE,        # Disables all interactivity (no hover, zoom, pan)
    displayModeBar = FALSE,   # Hides the plotly toolbar
    editable = FALSE,         # Disables annotations and editing
    showTips = FALSE,         # Removes tooltip on hover
    displaylogo = FALSE,      # Hides plotly logo
    responsive = FALSE        # Disables responsive resizing
  )

## High-d vis model
df_exe <- comb_data_model(
    highd_data = scurve, 
    model_highd = df_bin_scurve, 
    model_2d = df_bin_centroids_scurve
)

df <- df_exe |>
    dplyr::filter(type == "data") ## original dataset

df_b <- df_exe |>
  dplyr::filter(type == "model") ## High-d model

scurve_umap_model_vis <- langevitour::langevitour(df_exe[1:(length(df_exe)-1)],
                         lineFrom = tr_from_to_df_scurve$from,
                         lineTo = tr_from_to_df_scurve$to,
                         group = df_exe$type,
                         pointSize = append(rep(2, NROW(df_b)), rep(1, NROW(df))),
                         levelColors = c("#000000", "#33a02c"),
                         enableControls = FALSE,
                         width = "421px", height = "421px")

## Generate 2D projections

@@

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   hex_grid_scurve_int,
                  htmltools::div(
                    style = "margin-top: 13px;",  # adjust px as needed
                    scurve_umap_model_vis
                  )),
    device = "xs"
  )
```

```{r, eval=knitr::is_latex_output()}

@@

```{r, eval=knitr::is_latex_output()}
